Project 2

### 2015-03-31 project2/paper/main.tex
Adding a little more to the caveat section

\section{Technology Used}

>>>>

For individual trains, we'll also ignore some of the micro-effects of acceleration and deceleration and assume our
between station times measurements captures that. For visualization purposes, we can simply draw trains as moving at a
constant velocity through the system, although this is clearly not the case.

\section{Technology Used}
The simulation was built using CoffeeScript \cite{coffeescript}, using Backbone \cite{backbone}, Underscore
\cite{underscore} and jQuery \cite{jQuery} to organize code some. Code was bundled via Browserify \cite{browserify},
and minified with UglifyJS \cite{uglify}. Gulp \cite{gulp} was used as a build tool and package management was done
via NPM \cite{npm}.
